Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-17 paper/paper.tex
Keeping abstract simple

	The best known deterministic algorithm known so far was $O(k^2\cdot \ell^2)$-competitive \cite{repartition-disc},
	and the best known lower bound for the competitive ratio of
	deterministic algorithms was $\Omega(k)$,
 by reduction from online paging.
	  In this paper, we provide the lower bound of $\Omega(k\cdot \ell)$.
    We also present an optimal algorithm for the case of $k=3$.
  Finally,
  we provide a $O(k\cdot \ell)$-competitive algorithm for the variant
  where the optimal configuration is always a fixed partition
  that incurs zero communication cost through the whole request sequence.
\end{abstract}

>>>>

  So far, the best known lower bound for the competitive ratio of
	deterministic algorithms was $\Omega(k)$,
 by reduction from online paging.
  We improve this result significantly by providing the lower bound of $\Omega(k\cdot \ell)$.
  We follow up with an optimal algorithm for $k=3$.
  Finally,
  we provide a $O(k\cdot \ell)$-competitive algorithm for the variant
  where the optimal configuration is always a fixed partition
  that incurs zero communication cost through the whole request sequence.
\end{abstract}
